### 2022-05-30 README.Rmd
corrected date format

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Bayesian inference of prehistoric population dynamics from multiple proxies: a case study from the North of the Swiss Alps"
```

>>>>

```{r, echo = FALSE}
invisible(Sys.setlocale("LC_TIME",'C'))
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Bayesian inference of prehistoric population dynamics from multiple proxies: a case study from the North of the Swiss Alps"
```
